A data-intensive assessment of the species-abundance distribution.

### 2015-03-19 defense_pres.tex
Acknowledgements and accessibility.

\section{Conclusions}

@@

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{Acknowledgements}
~\\ %Adds vertical space for better aesthetics
Dr. Thomas Price \& USU Student Health Center
\end{frame}
\end{document}

>>>>

\section{Conclusions}
\begin{frame}{}
~\\ 
\frametitle{Conclusions}\
Challenging to infer process from species abundance distributions alone.
~\\ 
\begin{itemize}
\item Multiple mechanisms proposed for each SAD formulation.
\item Broad model categorization (i.e. neutral or non-neutral) may be more productive.
\item May not be one single suite of processes that dominates.
\end{itemize} 
\end{frame}

\begin{frame}[t]{}
\frametitle{Conclusions}\
~\\ 
Challenges in identifying mechanism among datasets.
~\\ 
\begin{itemize}
\item Biological vs. non-biological differences (spatial structuring, sampling intensity).
\item Diverse data removes uncertainty about non-biological pattern generating mechanisms.
\item Even with a great deal of data, identifying mechanism is still challenging.
\end{itemize} 
\end{frame}

\begin{frame}[t]{}
\frametitle{Conclusions}\
~\\ 
\begin{large}
Predictive macroecology
\end{large}
~\\ 
\begin{itemize}
\item Traditional approach is pattern to process to prediction.
\item May be possible to generate robust ecological predictions from general patterns.
\item Process and prediction may be two separate research goals.
\end{itemize} 
\end{frame}

@@

\begin{frame}[t]{}
\frametitle{Acknowledgements}
~\\ %Adds vertical space for better aesthetics
Dr. Thomas Price \& USU Student Health Center.\\
~\\
The Flint Hills of Kansas.\\
~\\
Tea, electric blankets, \& heating pads.\\
~\\
A very supportive husband \& family.\\
\end{frame}

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{Accessibility}
\begin{flushright}
This dissertation brought to you by:
\end{flushright}
\begin{Large}
Disability accommodations\\
\end{Large}
~\\
\begin{itemize}
\item Remote access \& participation.\\
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}
\end{itemize}
\end{frame}

\end{document}
